Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-10-14 paper/paper.Rmd
add some more context to similarity of repeated executions for spcv_env and sptcv_cluto

<!-- only some methods are suited for repeated execution -->
<!-- spcv_coords: limited variance due to limited k-means possibilities -->
CV is often executed repeatedly to reduce the possible influence of random variability on CV estimates.
In general, only methods that involve a random mechanism for generating or resampling blocks are suited for this.
In leave-one-block-out CV, coordinate-based and environmental clustering (`"spcv_coords"`, `"spcv_env"` and `"sptcv_cluto"`) achieve this as their clusters are generated based on random seeds.
However, experience with `"spcv_coords"` shows that clusters from repeated executions may in some situations be nearly identical to each other, resulting in very little variability between CV repetitions.
This issue is even more critical in CV at the block level with `"spcv_block"` with options `selection = "systematic"` and `selection = "checkerboard"` because identical folds are assigned in each repetition.
In contrast, `"spcv_block"` with option `selection = "random"` avoids this problem.

>>>>

<!-- only some methods are suited for repeated execution -->
<!-- spcv_coords: limited variance due to limited k-means possibilities -->
CV is often executed repeatedly to reduce the possible influence of random variability on CV estimates.
In general, only methods that involve a random mechanism for generating or resampling blocks are suited for this.
In leave-one-block-out CV, coordinate-based and environmental clustering (`"spcv_coords"`, `"spcv_env"` and `"sptcv_cluto"`) achieve this as their clusters are generated based on random seeds.
However, experience with `"spcv_coords"` shows that clusters from repeated executions may in some situations be nearly identical to each other, resulting in very little variability between CV repetitions.
While this effect also depends on the variable used for clustering, similar effects could potentially also apply to `"spcv_env"` and `"sptcv_cluto"` methods.
However, such effects are more difficult to quantify because selected features of these methods are always different in contrast to `"spcv_coords"` which always uses coordinates for clustering.
This issue is even more critical in CV at the block level with `"spcv_block"` with options `selection = "systematic"` and `selection = "checkerboard"` because identical folds are assigned in each repetition.
In contrast, `"spcv_block"` with option `selection = "random"` avoids this problem.
